maze-dataset: Maze Generation with Algorithmic Variety and Representational Flexibility

### 2025-08-04 docs/paper/paper.tex
narrowed it down to figs 4, 6, 7, 8 and tab 1 are the issue in paper compilation

Datasets of mazes are created from a
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDatasetConfig}{\texttt{MazeDatasetConfig}}
configuration object, which allows specifying the number of mazes, their
size, the generation algorithm, and various parameters for the
generation algorithm. Datasets can also be filtered after generation to
satisfy certain properties. Custom filters can be specified, and some
filters are included in
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/dataset/filters.html\#MazeDatasetFilters}{\texttt{MazeDatasetFilters}}

@@

Autoregressive transformer models can be quite sensitive to the exact
format of input data, and may even use delimiter tokens to perform
reasoning steps (\citeproc{ref-pfau2024dotbydot}{Pfau et al., 2024};
\citeproc{ref-spies2024causalworldmodels}{Spies et al., 2024}). To
facilitate systematic investigation of the effects of different
representations of data on text model performance, we provide a variety
of text output formats, with an example given in
\autoref{fig:token-regions}.

\input{figures/tex/fig4_tokenfmt.tex}

@@

\input{figures/tex/tab1_benchmarks.tex}

\input{figures/tex/fig6_benchmarks.tex}

\input{figures/tex/fig7_sre.tex}

@@

\input{figures/tex/fig8_impl.tex}

@@

@@

@@

@@

@@

@@

>>>>

Datasets of mazes are created from a
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDatasetConfig}{\texttt{MazeDatasetConfig}}
configuration object, which allows specifying the number of mazes, their
size, the generation algorithm, and various parameters for the
generation algorithm. Datasets can also be filtered after generation to
satisfy certain properties. Custom filters can be specified, and some
filters are included in
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/dataset/filters.html\#MazeDatasetFilters}{\texttt{MazeDatasetFilters}}.

@@

Autoregressive transformer models can be quite sensitive to the exact
format of input data, and may even use delimiter tokens to perform
reasoning steps (\citeproc{ref-pfau2024dotbydot}{Pfau et al., 2024};
\citeproc{ref-spies2024causalworldmodels}{Spies et al., 2024}). To
facilitate systematic investigation of the effects of different
representations of data on text model performance, we provide a variety
of text output formats, with an example given in
\autoref{fig:token-regions}. We utilize Finite State Transducers
(\citeproc{ref-Gallant2015Transducers}{Gallant, 2015}) for efficiently
storing valid tokenizers.

@@

@@

Our package is implemented in Python(\citeproc{ref-python}{Rossum,
1995}), and makes use of the extensive scientific computing ecosystem,
including NumPy (\citeproc{ref-numpy}{Harris et al., 2020}) for array
manipulation, plotting tools (\citeproc{ref-matplotlib}{Hunter, 2007};
\citeproc{ref-seaborn}{Waskom, 2021}), Jupyter notebooks
(\citeproc{ref-jupyter}{Kluyver et al., 2016}), and PySR
(\citeproc{ref-pysr}{Cranmer, 2023}) for symbolic regression.

@@

\bibitem[\citeproctext]{ref-pysr}
Cranmer, M. (2023). Interpretable machine learning for science with PySR
and SymbolicRegression. jl. \emph{arXiv Preprint arXiv:2305.01582}.
\url{https://doi.org/10.48550/arXiv.2305.01582}

@@

\bibitem[\citeproctext]{ref-Gallant2015Transducers}
Gallant, A. (2015). \emph{Index 1,600,000,000 keys with automata and
rust}. \url{https://burntsushi.net/transducers/}.

@@

\bibitem[\citeproctext]{ref-numpy}
Harris, C. R., Millman, K. J., Walt, S. J. van der, Gommers, R.,
Virtanen, P., \& al., et. (2020). Array programming with NumPy.
\emph{Nature}, \emph{585}, 357--362.
\url{https://doi.org/10.1038/s41586-020-2649-2}

\bibitem[\citeproctext]{ref-matplotlib}
Hunter, J. D. (2007). Matplotlib: A 2D graphics environment.
\emph{Computing in Science and Engineering}, \emph{9}(3), 90--95.
\url{https://doi.org/10.1109/MCSE.2007.55}

@@

\bibitem[\citeproctext]{ref-jupyter}
Kluyver, T., Ragan-Kelley, B., Perez, F., Granger, B., Bussonnier, M.,
Frederic, J., Kelley, K., Hamrick, J., Grout, J., Corlay, S., Ivanov,
P., Avila, D., Abdalla, S., \& Willing, C. (2016). Jupyter notebooks - a
publishing format for reproducible computational workflows.
\emph{Proceedings of the 20th International Conference on Electronic
Publishing}, 87--90. \url{https://doi.org/10.3233/978-1-61499-649-1-87}

@@

\bibitem[\citeproctext]{ref-python}
Rossum, G. van. (1995). \emph{Python reference manual} (CS-R9525).
Centrum voor Wiskunde; Informatica (CWI).
\url{https://ir.cwi.nl/pub/5008/05008D.pdf}

@@

\bibitem[\citeproctext]{ref-seaborn}
Waskom, M. L. (2021). {seaborn}: Statistical data visualization.
\emph{Journal of Open Source Software}, \emph{6}(60), 3021.
\url{https://doi.org/10.21105/joss.03021}
